% !TEX root = ../main.tex
\chapter{Introduction}

The year is 2025, fourteen years since the inception of the handwritten \textit{Ulus} conlang, an ancient precursor of Mazulia. \textit{Ulus}, a personal cryptic conlang, was inspired by Turkish, Arabic, and Indonesian and was written in Caucasus-styled Cyrillic. In the next couple of years, from the influence of learning hundreds of languages, \textit{Ulus} have undergone significant changes in phonology, orthography, and styling – particularly from Romanian and Russian. The conlang evolved particularly quicker since the author's encounter with another conlanger from Thailand in 2017. At that time, it was renamed into \textit{T'aalamuri} (\textit{t'aal} < \textsc{Dutch} \textit{taal} 'language', \textit{uri} < \textsc{Korean} \textit{uri} 'we' $\equiv$ \textit{'Our Language'}) and had a pseudo-complete grammar compiled. By the time, \textit{T'aalamuri} already had 1,002 lexical units and around 2,200 grammatical morphemes. Further development in all aspects of the conlang caused it to evolve into \textit{Malhuri}, \textit{Malhivaa}, \textit{Ulemaiśxa}, \textit{Ulemanxa}/\textit{Churzit-Qolmalandy}, and \textit{Qarghicinva}/\textit{Qaiva} before receiving its final name in 2020, Mazulia. Since then, Mazulia has perfected even more subsantially to enhance the natural feel of the language.

The author has lived almost entirely in an ultraconservative authoritarian society where freedom of expression is practically inexistent. Mazulia was intended to be a personal language to express the author's opinions in a rather cryptic format so that only a select number of readers could access the knowledge behind, but lately it has become a more of artistic language for the worldbuilding project. Yet, the nature of secrecy still prevails in some degree.

\section{Mazulia and Amqala}

\section{History}

\section{Outline of Features}

\section{Real-World Use}